### 2020-01-10 ChapterIntroduction/chapterIntroduction.tex
Updated: Outline of thesis included in Introduction

\chapter{Introduction}
Video games rely on real-time physics engines to provide realistic environments. This is noticeable in 3D gaming where players expect fast paced interaction. This requirement has produced significant commercial activity resulting in physics engines for real-time simulation for rigid body dynamics. Although realism is convincing, a degree of mathematical accuracy is usually sacrificed (causing error) in order to attain real-time delivery within constrained resource settings. However, with significant commercial effort, the mathematical error has reduced over the years and commercial game engines are finding their use in other industries (e.g.,  \cite{Xu2017, Lu2017, Shah2018}).

@@

\section{Purpose of Study}
\section{Outline}

>>>>

\chapter{Introduction}

\section{Overview}
Video games rely on real-time physics engines to provide realistic environments. This is noticeable in 3D gaming where players expect fast paced interaction. This requirement has produced significant commercial activity resulting in physics engines for real-time simulation for rigid body dynamics. Although realism is convincing, a degree of mathematical accuracy is usually sacrificed (causing error) in order to attain real-time delivery within constrained resource settings. However, with significant commercial effort, the mathematical error has reduced over the years and commercial game engines are finding their use in other industries (e.g.,  \cite{Xu2017, Lu2017, Shah2018}).

@@

\section{Purpose of Study}
%Can scalable real-time physics be acheived?
%Can collisions between objects always remain correct in AP?

\section{Outline}
2. Background and Related Work:
\begin{itemize}
	%Context
	\item Real-time physics engines overview. Introduce the reader to the topic of physics simulations. Comparison with non-real-time physics simulations. Define terms, workings, important and relevant aspects, e.g. body types, uses in games and simulations, typical scales and performance and performance budget.
	\item Online gaming. Wider topic of online gaming (client-hosted, P2P, server), challenges of latency, security/cheating and computational limits.
	\item Physics in online gaming (lack of due to challenges)
	%Relevant Related Work
	\item Graph-partitioning. When it comes to spatially-partitioning a simulation, the problem is essentially a graph partitioning problem, where objects are nodes and if there's a possible interaction, an edge exists. Useful for terms, comparisons with and future work on load-balancing will heavily involve this.
	\item Distributed virtual environments, old way of distributing game worlds, some similar approaches (migratory), but most settled on non-migratory and the reasons why non-migratory worked better for those and migratory is required for AP.
	%Applications
	\item Scientific and Engineering simulations. Real-time simulations are being used more in scientific research, however these are limited to what can be achieved on a single machine. AP allows real-time physics simulations to scaled, allowing simulations that otherwise wouldn't have been able to, run in real-time.
	\item Containerisation of Game Engines. Game engines, generally, currently run as one single application (with the exception of  databases), including graphics, physics, AI etc. AP separates out the physics element into its own container, much like many modern systems are splitting up different aspects of systems into their own containers. This containerisation of physics, means, physics can be elastically scaled independently from other systems such as graphics.
	\item Streamed Gaming. The main foreseeable application of AP is Streamed Gaming. Large multi-player worlds, persistent and scalable. Dedicated and elastic physics nodes. Physics is no longer limited to what can be simulated on a single machine. Co-located render nodes solves the issue of higher latencies between the render node and physics simulation. 
\end{itemize}

3. Problem Definition:
\begin{itemize}
	\item Naive approach. How would a naive approach behave and what problems occur.
	\item Considered Solutions. We consider a number of solutions to scalable real-time physics.
	\item Proposed Solution. We look at in more detail how our solution works and justification for its choice.
	\item Aura Calculation. A detailed look at the important aspect of AP, the aura calculation.
	\item Sub-optimal object hosting. We look at one the predicted challenge with AP, sub-optimal object hosting and discuss a solution which can be addressed in future work.
	\item Thrashing. A further predicted challenge with AP, this consists of two types of thrashing, two and three object thrashing, three object thrashing has been solved in this implementation of AP and we discuss solutions to two object thrashing.
	\item Islands. A solved challenge with AP, here we discuss our solution.
	\item Corner Case. AP has been discussed in terms of a single boundary between two servers up to this point, but in order for a general solution to be achieved, AP must be able to support boundaries between three or more servers, such as at corners.
\end{itemize}

4. Implementation
\begin{itemize}
	\item System Architecture. We discuss how the system is organised. How AP interacts with PhysX. How messages are exchanged between servers using RakNet and how the client communicates with the servers, enabling interaction.
	\item Algorithms. The algorithms used by AP are defined with pseudo-code and explained.
\end{itemize}

5. Experiments and Results
\begin{itemize}
	\item Scalability Experiments. We describe and justify the design of experiments designed to address the first question of this thesis: Can scalable real-time physics simulations be achieved? AP's performance is measured with different numbers of servers in different topologies. The results of which, are analysed and discussed.
	\item Collisions Correctness Experiments. Collisions correctness is defined and erroneous collisions are classified. We describe and justify the design of experiments designed to address the second question of this thesis: Can real-time physics simulations remain correct when scaled? The correctness of collisions are measured using different conditions and tolerances. The results of which, are analysed discussed.
\end{itemize}

6. Conclusion and Future Work
\begin{itemize}
	\item Conclusion. The results and findings of our experiments are used to answer the questions asked in this thesis: "Can scalable real-time physics simulations be achieved?" and "Can real-time physics simulations remain correct when scaled?"
	\item Future Work. We discuss future questions regarding scalable real-time physics and future implementation plans for AP.
\end{itemize}
